### 2023-04-10 chapter2/chapter2_supporting.tex
Added rate histogram to chapter 2 supplement

>>>>

\begin{figure}[h!]
\includegraphics[width=0.75\textwidth]{scores/out/scores_histogram.png}
\centering
\caption{\textbf{Histogram of disorder score rates in regions.}
The grey interval indicates the upper decile of the distribution across both disorder and order regions, which was used as the input set for the GO term enrichment analysis.}
\label{sfig:scores_histogram}
\end{figure}
